---
title: "The `charpente` framework"
knitr:
  opts_chunk: 
    collapse: true
    comment: ""

editor: 
  render-on-save: true
    
execute:
  echo: true
  warning: false
  eval: false
---

```{r}
#| label: utils
#| eval: true 
#| echo: false 
#| include: false
source("_common.R")
```

[`charpente`](https://rinterface.github.io/charpente/) apps use similar to standard R packages (i.e., they use `devtools` and `usethis`), but they're designed to '*significantly reduce the complexity of creating new HTML templates for Shiny*':[^view-cap]

[^view-cap]: Download the code used to build the `charpente` app [here](https://github.com/mjfrigaard/sfw/raw/main/_apps/cap.tar.gz)

## Getting started

For a more complete introduction to the `charpente` package, I recommend [chapter 21](https://unleash-shiny.rinterface.com/workflow-charpente#workflow-charpente) of [Outstanding User Interfaces with Shiny](https://www.routledge.com/Outstanding-User-Interfaces-with-Shiny/Granjon/p/book/9780367643652) by David Granjon. 

Create a `charpente` using the `create_charpente()`:

```{r}
#| label: create_charpente
#| code-fold: false
#| eval: false
create_charpente(getwd(), license = "mit")
```

```{bash}
#| label: create_charpente-cap-desc
#| eval: false
#| code-fold: false
✔ Setting active project to '/Users/username/apps/cap'
✔ Creating 'R/'
✔ Writing 'DESCRIPTION'
Package: cap
Title: What the Package Does (One Line, Title Case)
Version: 0.0.0.9000
Authors@R (parsed):
    * Martin Frigaard <mjfrigaard@pm.me> [aut, cre]
Description: What the package does (one paragraph).
License: `use_mit_license()`, `use_gpl3_license()` or friends to
    pick a license
Imports:
    htmltools,
    shiny,
    utils
Encoding: UTF-8
Roxygen: list(markdown = TRUE)
RoxygenNote: 7.3.1
```

```{bash}
#| label: create_charpente-files
#| eval: false
#| code-fold: false
✔ Writing 'NAMESPACE'
✔ Writing 'cap.Rproj'
✔ Adding '^cap\\.Rproj$' to '.Rbuildignore'
✔ Adding '.Rproj.user' to '.gitignore'
✔ Adding '^\\.Rproj\\.user$' to '.Rbuildignore'
✔ Setting active project to '<no active project>'
✔ Package 'cap' successfuly created!
✔ Setting active project to '/Users/username/apps/cap'
✔ Adding 'MIT + file LICENSE' to License
✔ Writing 'LICENSE'
✔ Writing 'LICENSE.md'
✔ Adding '^LICENSE\\.md$' to '.Rbuildignore'
✔ Writing 'cran-comments.md'
✔ Adding '^cran-comments\\.md$' to '.Rbuildignore'
✔ Writing 'README.md'
• Update 'README.md' to include installation instructions.
✔ Writing 'CODE_OF_CONDUCT.md'
✔ Adding '^CODE_OF_CONDUCT\\.md$' to '.Rbuildignore'
• You may also want to describe the code of conduct in your README:
  ## Code of Conduct
  
  Please note that the dev project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
  [Copied to clipboard]
✔ Writing 'NEWS.md'
✔ Adding CRAN status badge to 'README.md'
✔ Adding Lifecycle: experimental badge to 'README.md'
✔ Adding 'testthat' to Suggests field in DESCRIPTION
✔ Adding '3' to Config/testthat/edition
✔ Creating 'tests/testthat/'
✔ Writing 'tests/testthat.R'
• Call `use_test()` to initialize a basic test file and open it for editing.
✔ Writing 'tests/testthat/test-dummy-test.R'
• Edit 'tests/testthat/test-dummy-test.R'
✔ Installed "`esbuild`", "`esbuild-sass-plugin`", "`postcss`", "`autoprefixer`" 
✔ Adding '^srcjs$', '^node_modules$', '^package\\.json$', '^package-lock\\.json$', '^styles$', '^esbuild\\.cap\\.js$', '^esbuild\\.prod\\.js$' to '.Rbuildignore'
✔ Adding 'node_modules' to '.gitignore'
✔ Installed "`mocha`" 
✔ Initialising Git repo
✔ Adding '.Rhistory', '.Rdata', '.httr-oauth', '.DS_Store', '.quarto' to '.gitignore'
```

```{bash}
#| label: create_charpente-git-commit
#| eval: false
#| code-fold: false
There are 17 uncommitted files:
* '.gitignore'
* '.Rbuildignore'
* 'CODE_OF_CONDUCT.md'
* 'cran-comments.md'
* 'DESCRIPTION'
* 'cap.Rproj'
* 'LICENSE'
* 'LICENSE.md'
* 'NAMESPACE'
* 'NEWS.md'
* ...
Is it ok to commit them?

1: Absolutely not
2: No way
3: Yeah

Selection: 2
Warning: Opening new project in a new session ...
```

## Package files 

## Building charpente apps

## Dependencies 

## Recap

