---
title: "shiny-app-frameworks"
format:
  html: 
    toc: true
    toc-depth: 5
    toc-location: right
    toc-title: Contents
    
  
knitr:
  opts_chunk: 
    collapse: true
    comment: "\t"
---

<!-- https://gist.github.com/jthomasmock/11acebd4448f171f786e01397df34116 -->

```{r}
#| label: setup 
#| warning: false 
#| message: false
#| echo: false 
#| include: false
options(repos = "http://cran.us.r-project.org")
```

```{r}
#| label: pak_setup
#| warning: false 
#| message: false
#| echo: false
# see if pak is on the names of the loaded namespaces
if (isFALSE("pak" %in% loadedNamespaces())) {
  install.packages("pak", quiet = TRUE)
} 
library(pak)
```

### Shiny frameworks

This website is a resource for developers who are curious about the relative pros and cons of using a Shiny framework to build their apps.

This repo contains the following shiny applications: 

1. [`gap`](https://github.com/mjfrigaard/sfw/tree/main/_apps/gap): a `golem` app-package

2. [`lap`](https://github.com/mjfrigaard/sfw/tree/main/_apps/lap): a `leprechaun` app-package

3. [`rap`](https://github.com/mjfrigaard/sfw/tree/main/_apps/rap): a `rhino` app (pseudo-package)[^rhino-non-pkg]

[^rhino-non-pkg]: `rhino` apps aren't R packages--they're dependencies are managed with a `dependencies.R` file and [`box`](https://klmr.me/box/) modules.

### The application

The original data and code for each application comes from [Building Web Applications With Shiny](https://rstudio-education.github.io/shiny-course/)[^bwas], but has been adapted to provide a basic (but realistic) example with modules, utility function, tests, etc.

[^bwas]: This was a popular course among colleagues and covers (in my opinion) what a developer should know before considering a framework.