---
title: "shiny-app-frameworks"
format:
  html: 
    toc: true
    toc-depth: 5
    toc-location: right
    toc-title: Contents
    
  
knitr:
  opts_chunk: 
    collapse: false
    comment: "\t"
---

<!-- https://gist.github.com/jthomasmock/11acebd4448f171f786e01397df34116 -->

## Motivation

This repo contains the following shiny applications: 

1. [`gap`](https://github.com/mjfrigaard/sfw/tree/main/_apps/gap): a `golem` app-package

2. [`lap`](https://github.com/mjfrigaard/sfw/tree/main/_apps/lap): a `leprechaun` app-package

3. [`rap`](https://github.com/mjfrigaard/sfw/tree/main/_apps/rap): a `rhino` app (pseudo-package)

3. [`duap`](https://github.com/mjfrigaard/sfw/tree/main/_apps/duap): a `devtools`/`usethis` app-package

```{r}
#| eval: false
#| echo: false
if ("pak" %in% loadedNamespaces()) {
  pak_update(stream = "devel")
} else {
  install.packages("pak", quiet = TRUE)
}
```

### Dependencies 

One of the constant concerns for developers is relying on an experimental or 'new' add-on package, that code changing, and something we built that used to work is now breaking.

All shiny app-packages depend on `shiny` and `devtools`, so adding more dependencies can make developers uneasy. 

### `devtools` dependencies 

```{r}
#| code-fold: show 
#| code-summary: 'show/hide devtools dependencies'
#| eval: true
#| echo: true 
#| collapse: true
pak::pkg_deps_tree(pkg = "devtools", dependencies = TRUE)
```

